---
title: "Thesis missing data and relational event model"
output: html_document
date: "2023-05-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Libraries
```{r}
library(mice)     
library(purrr)    
library(furrr)    
library(mvtnorm)  
library(magrittr) 
library(dplyr)    
library(tibble)   
library(relevent)
library(Epi)
library(ggplot2)
library(sna)
library(remify)
library(RSiena)
library(rem)
library(survival)
library(remstats)
library(remify)
library(igraph)
library(visNetwork)
```

```{r}
devtools::install_github("TilburgNetworkGroup/remstats@v3.1.0")
devtools::install_github(repo = "TilburgNetworkGroup/remstimate")
devtools::install_github("TilburgNetworkGroup/remify")
```

# Explore the data

```{r}
load("~/Master Applied Data Science/Thesis/Thesis/UUsummerschool.Rdata")
str(PartOfApollo_13)
summary(PartOfApollo_13)
head(PartOfApollo_13)
```
## Visualize the network

```{r}
#build the network
edges<-data.frame(from=c(as.character(PartOfApollo_13[,2])),to=c(as.character(PartOfApollo_13[,3])))
Apollo<-graph_from_data_frame(edges,directed = TRUE)
summary(Apollo)

#function to visualize the real network (with interaction)
set.seed(100)
Apollo_interactive_layout<-visNetwork(data.frame(id=V(Apollo)$name), edges, main = "Apollo",submain="Can zoom in/out to check the IDs and ties") %>%
  visIgraphLayout(layout = "layout_nicely",smooth =  FALSE) %>%
  visNodes(shape="circle",label = TRUE) %>% 
  visOptions(highlightNearest = list(enabled = T, hover = T), nodesIdSelection = T)

Apollo_interactive_layout 
```


### Centrality measures

```{r}
#function to calculate centrality metrics
find_highest_centrality <- function(graph){
  
  # highest degree
  degree <- degree(graph, mode = "all")
  node_degree <- V(graph)$name[which.max(degree)]
  
  # highest betweenness
  betweenness <- betweenness(graph, normalized = TRUE)
  node_betweenness <- V(graph)$name[which.max(betweenness)]
  
  # highest closeness
  closeness <- closeness(graph, mode = "all")
  node_closeness <- V(graph)$name[which.max(closeness)]
  
  # highest eigenvector
  eigen_centrality <- eigen_centrality(graph)$vector
  node_eigen <- V(graph)$name[which.max(eigen_centrality)]
  
  # combine results
  cat("Highest degree is node: ", node_degree, "\n")
  cat("Highest betweenness is node: ", node_betweenness, "\n")
  cat("Highest closeness is node: ", node_closeness, "\n")
  cat("Highest eigenvector is node: ", node_eigen, "\n")
}

find_highest_centrality(Apollo)
```
# Missing Data Part

## Impute missing data and fill in for 3 sims

```{r ampute and impute for 3 sims}

Apollo_tibble <- as_tibble(PartOfApollo_13)

mbased_finite_apollo <- list(
  MCAR = furrr::future_map(1:3, ~ { # map over 3 sims
    Apollo_tibble %>% 
      ampute(prop = .2, 
             mech = "MCAR", patterns = c(1,1,0)) %>% .$amp %>% 
      mice(m = 5, 
           maxit = 5,
           method = "pmm",
           print = F)
  }  , .options = furrr_options(seed = 123)),
  MAR = furrr::future_map(1:3, ~ { # map over 3 sims
    Apollo_tibble %>% 
      ampute(prop = .2, 
             mech = "MAR", patterns = c(1,1,0), type = "RIGHT") %>% .$amp %>% 
      mice(m = 5, 
           maxit = 5,
           method = "pmm",
           print = F)
  }, .options = furrr_options(seed = 123))
)

```

## Single Amputation

```{r single amputation}
MCAR_single <- ampute(Apollo_tibble, prop = .2, 
                      mech = "MCAR", patterns = c(1,1,0))

head(MCAR_single$amp)
```

## Analysis single amputation

### How much missing points in receiver 
```{r}
ini <- mice(MCAR_single$amp, maxit = 0)
ini$nmis
```
### Plot pattern missing data

```{r}
md.pattern(MCAR_single$amp)
```
### Flux plot
```{r}
fx <- fluxplot(MCAR_single$amp)
```

## Imputation missing values 

```{r}
mids <- mice(MCAR_single$amp, m = 5, 
                        maxit = 5,
                        method = "pmm",
                        print = F)

# removing time as a predictor
pred <- mids$pred
pred[ ,"time"] <- 0

imp <- mice(MCAR_single$amp, m=5, 
                        maxit=5,
                        pred=pred,  
                        method = "pmm", 
                        print=F)


```

```{r}
# check if there are no loops
mids |>
  complete("long") |>
  summarize(all(sender != receiver))
```

### Inspect imputation
```{r}
bwplot(mids)
```


### Density plot imputation receiver column
```{r}
densityplot(mids, lwd = 3)
```



### Scatterplot: Impact of imputation method on sender and receiver in MCAR_single_imp.
```{r}
xyplot(mids, receiver ~ sender | .imp)
```

# REM Part

## REM on the original dataset

### StatsObject 

```{r}
apollo.renamed <- PartOfApollo_13
apollo.renamed <- apollo.renamed %>% 
  rename(
    actor1 = sender,
    actor2 = receiver
  )


# Define effects
effects <- ~ -1 + reciprocity() + indegreeSender() + outdegreeReceiver()

# Prepare event history
reh <- remify::remify(edgelist = apollo.renamed, model = "tie")

# Compute statistics
statsObject <- remstats(reh = reh, tie_effects = effects)
dim(statsObject)
head(attr(statsObject, "riskset"))

# Estimate model parameters
fit <- remstimate::remstimate(reh = reh, stats = statsObject,
                              method = "MLE")
summary(fit)
```

### Function to create data for coxph 

```{r}
prepare_coxph_data_single <- function(statsObject, apollo) {
  # Extract risk sets and remove 'id' column
  risk_sets <- attr(statsObject, "riskset")
  risk_sets <- risk_sets %>% select(-'id')
  
  # Get the times
  time <- apollo$time
  
  # merge riskset with each timepoint
  combined <- merge(risk_sets, time, by = NULL)
  
  combined <- combined %>% rename("time" = "y")
  combined <- lapply(combined, as.numeric)
  combined <- as.data.frame(combined)
  
  # Create matrices for subtraction to make a status column for coxph
  combined_matrix <- data.matrix(combined)
  matrix_rows <- nrow(combined)
  
  repeated_df <- apollo[rep(seq_len(nrow(apollo)), each = 240), ] 
  repeated_df <- repeated_df[, c(2,3,1)]
  
  apollo_matrix <- data.matrix(repeated_df)
  status_matrix <- apollo_matrix - combined_matrix
  
  # create a status column
  status <- as.integer(rowSums(status_matrix == 0) == ncol(status_matrix))
  status <- as.data.frame(status)
  
  # Add status to the combined set
  combined <- cbind(combined, status)
  
  # Extract statistics and add them to the dataframe
  reciprocity <- statsObject[,,1]
  indegreeSender <- statsObject[,,2]
  outdegreeReceiver <- statsObject[,,3]
  
  combined$reciprocity <- c(reciprocity)
  combined$indegreeSender <- c(indegreeSender)
  combined$outdegreeReceiver <- c(outdegreeReceiver)
  
  return(combined)
}

# Coxp data original dataset
coxph_data_original <- prepare_coxph_data_single(statsObject, PartOfApollo_13)

coxph_data_original
```

### Coxph analysis

```{r}
cox_t <- coxph(Surv(time, status) ~ reciprocity + indegreeSender + outdegreeReceiver, data=coxph_data_original)

cox_t

```


## REM on the imputed datasets

### Function to create StasObject

```{r}
analysis_function <- function(data) {
  # Rename columns
  data <- data %>% 
    rename(
      actor1 = sender,  # replace 'sender' with the correct column name
      actor2 = receiver  # replace 'receiver' with the correct column name
    )

  # Perform the analysis as before
  reh <- remify::remify(edgelist = data, model = "tie")
  statsObject_imp <- remstats(reh = reh, tie_effects = effects)

  # Return the fit
  return(statsObject_imp)
}

imputed_data <- mice::complete(imp, "all")

statsObject_imp <- lapply(imputed_data, analysis_function)
```


### Function to create datasets for coxph

```{r}
# Define a function that prepares data for coxph
prepare_coxph_data <- function(statsObject_imp, apollo) {
  risk_sets <- attr(statsObject_imp, "riskset")
  risk_sets <- risk_sets %>% select(-'id')

  # Get the times
  time <- apollo$time

  # merge riskset with each timepoint
  combined <- merge(risk_sets, time, by = NULL)
  
  combined <- combined %>% rename("time" = "y")
  combined <- lapply(combined, as.numeric)
  combined <- as.data.frame(combined)

  # Create matrices for subtraction to make a status column for coxph
  combined_matrix <- data.matrix(combined)
  matrix_rows <- nrow(combined)
  
  repeated_df <- apollo[rep(seq_len(nrow(apollo)), each = 240), ] 
  repeated_df <- repeated_df[, c(2,3,1)]
  apollo_matrix <- data.matrix(repeated_df)
  
  status_matrix <- apollo_matrix - combined_matrix

  # create a status column
  status <- as.integer(rowSums(status_matrix == 0) == ncol(status_matrix))
  status <- as.data.frame(status)
  
  # Add status to the combined set
  combined <- cbind(combined, status)
  
  # Extract statistics and add them to the dataframe
  reciprocity <- statsObject_imp[,,1]
  indegreeSender <- statsObject_imp[,,2]
  outdegreeReceiver <- statsObject_imp[,,3]
  
  combined$reciprocity <- c(reciprocity)
  combined$indegreeSender <- c(indegreeSender)
  combined$outdegreeReceiver <- c(outdegreeReceiver)
  
  return(combined)
}

```

### Coxph analysis

```{r}
# Apply the function to each imputed dataset
coxp_data_imputed <- lapply(statsObject_imp, prepare_coxph_data, apollo = PartOfApollo_13)

coxp_data_imputed
```


### Coxph models 

```{r}
coxph_models <- lapply(coxp_data_imputed, function(df) {
  coxph(Surv(time, status) ~ reciprocity + indegreeSender + outdegreeReceiver, data = df)
})
coxph_models
```

```{r}
pool(coxph_models)
```
