---
title: "Working Doc - Thesis"
author: "Dominic Comerford"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    theme: cosmo
---

```{r, include = FALSE}
knitr::opts_chunk$set(message = FALSE)
```
##Loading Packages and Data
```{r, warning = FALSE}
##### Load packages
packages_to_install <- c("purrr", "furrr", "magrittr", "dplyr", 
                         "tibble", "data.table", "survival", "tidyverse", 
                         "devtools", "reprex", "styler", "igraph", "RColorBrewer",
                         "visNetwork", "relevent", "sna", "zoo", "imputeTS")

for (pkg in packages_to_install) {
  if (!require(pkg, character.only = TRUE)) {
    # If not, install the package
    install.packages(pkg)
  }
}

library(purrr, warn.conflicts = FALSE)    # for functional programming
library(furrr, warn.conflicts = FALSE)    # for functional futures
library(magrittr, warn.conflicts = FALSE) # for pipes
library(dplyr, warn.conflicts = FALSE)    # for data manipulation
library(tibble, warn.conflicts = FALSE)     # for tibbles
library(data.table, warn.conflicts = FALSE)   
library(survival, warn.conflicts = FALSE) # for REM analysis
library(tidyverse, warn.conflicts = FALSE)  
library(tidyr, warn.conflicts = FALSE)
library(reprex, warn.conflicts = FALSE)   # reproducible code
library(styler, warn.conflicts = FALSE)
library(igraph, warn.conflicts = FALSE)
library(RColorBrewer, warn.conflicts = FALSE)  
library(visNetwork, warn.conflicts = FALSE)
library(relevent, warn.conflicts = FALSE)  
library(sna, warn.conflicts = FALSE)
library(zoo, warn.conflicts = FALSE)
library(imputeTS, warn.conflicts = FALSE)


devtools::install_github("TilburgNetworkGroup/remify")
devtools::install_github("gerkovink/mice@match_conditional_current") 
devtools::install_github("TilburgNetworkGroup/remstats")

library(mice, warn.conflicts = FALSE)     # for imputation and amputation
library(remstats, warn.conflicts = FALSE) # for REM statistics
library(remify, warn.conflicts = FALSE)   # for converting
```


```{r, warning = FALSE}
##### Load data
con <- url("https://github.com/mshafieek/ADS-Missing-data-social-network/raw/main/literature_%20REM/Tutorial_REM_REH_DATA/UUsummerschool.Rdata")
load(con)
apollo <- PartOfApollo_13 %>% 
  rename(
    actor1 = sender,
    actor2 = receiver
  )
rm(Class, PartOfApollo_13, Twitter_data_rem3, WTCPoliceCalls, ClassIntercept, 
   ClassIsFemale, ClassIsTeacher, WTCPoliceIsICR, con, pkg)

head(apollo)
tail(apollo)
summary(apollo)
str(apollo)
```

#Descriptive network analysis
```{r}
edges_apollo <- data.frame(from=c(as.character(apollo[,2])),to=c(as.character(apollo[,3])))
graph_apollo <- graph_from_data_frame(edges_apollo,directed = TRUE)

net <- simplify(graph_apollo, remove.multiple = T) # remove multiple edges for snapshot network analysis
edge_density(net)

centr_clo(net, mode="all", normalized=T)$centralization
centr_betw(net, directed=T, normalized=T)$centralization
centr_eigen(net, directed=T, normalized=T)$centralization
transitivity(net, type="global")

diameter(net, directed=T)
mean_distance(net, directed=T)

```


```{r}
set.seed(0)
ApolloNet <- as.sociomatrix.eventlist(apollo, 19)
Figure_1 <- gplot(ApolloNet, jitter = TRUE, pad = .075,
              mode = "target",
              displaylabels = TRUE, label.pos = 0, label.cex = .75,
              boxed.labels = TRUE, label.pad = .5, 
              displayisolates = FALSE, vertex.cex=.6,
              arrowhead.cex = .75, edge.lwd = -.75, edge.col = "gray")
```
##Sufficient set & Missingness function
```{r, include=FALSE}
set.seed(123) # fix seed to realize a sufficient set
apollo <- as_tibble(apollo)
indic <- sample(1:nrow(apollo), 1500)
remify(apollo[indic, ], model = "tie") %>% dim() # check if 16 nodes
#### Combine the sufficient set and the incomplete set
make_missing <- function(x, indic) {
  x$time_index <- seq_len(nrow(x))
  sufficient <- x[indic, ]
  miss <- x[-c(indic), ] |>
    ampute(prop = 0.4, 
           mech = "MCAR",
           patterns = matrix(c(1,1,0,1, # missing in actor 2 (4th column is time_index)
                               1,0,1,1, # missing in actor 1
                               0,1,1,1, # missing in time
                               0,0,0,1, # missing in all
                               1,0,0,1, # missing in actor 1 + 2
                               0,1,0,1, # missing in time + actor 2
                               0,0,1,1  # missing in time + actor 1
                               ),
                             nrow=7, 
                             byrow=TRUE)) %>% 
    .$amp
  
  combined <- rbind(sufficient, miss)
  combined <- combined[order(combined$time_index), ]
  combined <- combined[-4] # remove time_index
  return(combined)
}
```
##Multiple imputation specification
```{r, include=FALSE}
whichcol <- c("", "actor2", "actor1") # Ensure that actor 1 != actor 2 in imputations
names(whichcol) <- colnames(apollo)
## predictor matrix
pred <- make.predictorMatrix(apollo)
#pred[ ,"time"] <- 0 # using time for imputation creates loops
## use the pmm.conditional method
method <- make.method(apollo)
#method[1] <- "norm" # imputation of time correct? Something Like Last Obs Carried Forward?
method[c(2,3)] <- "pmm.conditional"
## post squeeze time between min and max time
#post <- make.post(apollo)
#min(apollo$time)
#max(apollo$time)
#post["time"] <- "imp[[j]][, i] <- squeeze(imp[[j]][, i], c(11849.2, 50014.8))"
```

##Interpolate 'time' before MICE
```{r}
set.seed(123)
mbased_finite_apollo_miss <-
  furrr::future_map(1:100, ~ {   # start of with 10 simulations for testing
    make_missing(apollo, indic) }, .options = furrr_options(seed = 123))
md.pattern(mbased_finite_apollo_miss[[1]], rotate.names = TRUE)

```
##Impute time with interpolation (single imputation)
```{r}
for (i in 1:length(mbased_finite_apollo_miss)) {
  # Impute missing values in the 'time' column using na_interpolation
  mbased_finite_apollo_miss[[i]]$time <- na_interpolation(mbased_finite_apollo_miss[[i]]$time)
}
```

##Impute sender and receiver through MICE
```{r}
##### Model-based finite populations
# # Function for a single tibble
# apply_mice_to_tibble <- function(tibble) {
#   # Apply mice to the tibble
#   imp <- mice(as.data.frame(tibble),
#                        m = 5,
#                        maxit = 5,
#                        method = method,
#                        whichcolumn = whichcol,
#                        predictorMatrix = pred,
#                        print = FALSE)
#   # Return the imputed tibble
#   return(imp)
# }
# # Apply mice to each tibble in mbased_finite_apollo
# set.seed(123)
# mbased_finite_apollo <- lapply(mbased_finite_apollo_miss, apply_mice_to_tibble) # possible future_map()

mbased_finite_apollo <- 
  furrr::future_map(1:100, ~ {
  #data_frame <- as.data.frame(mbased_finite_apollo_miss[[.x]])
  mice(mbased_finite_apollo_miss[[.x]],
       m = 5, 
       maxit = 5,
       method = method,
       whichcolumn = whichcol,
       predictorMatrix = pred,
       print = FALSE)
}, .options = furrr_options(seed = 123))
```

```{r, echo=FALSE}
# ##### Missing data pattern of all simulations.
# missing_pattern <- mbased_finite_apollo %>%
#   map(~.x %>% .$data) %>%
#   do.call("rbind", .) %>%
#   md.pattern(rotate.names = TRUE)
# 
# plot_with_time <- plot(mbased_finite_apollo[[5]])
# plot_with_time
# stripplot_with_time <- stripplot(mbased_finite_apollo[[5]])
# stripplot_with_time
# 
# test <- complete(mbased_finite_apollo[[5]], action = 3, include = TRUE)
# test <- mbased_finite_apollo[[5]]
# 
# plot(mbased_finite_apollo[[5]])
# stripplot(mbased_finite_apollo[[5]])

```

##Defining REM effects and preparing data for Cox function
```{r, echo=FALSE}
##### Defining effects for the relational event model
effects <- ~ -1 + reciprocity(scaling = ("std")) + indegreeSender() + outdegreeReceiver()

##### Function to get the statistics of the previously defined effects.
stats_function <- function(data) {
  # remify the data
  reh <- remify::remify(edgelist = data, model = "tie")
  # calculate effect statistics
  statsObject_imp <- remstats(reh = reh, tie_effects = effects)
  # Return the statistics
  return(statsObject_imp)
}
```


```{r}
##### Function for making the data compatible with coxph()
prepare_coxph_data <- function(statsObject, apollo) {
  risk_sets <- attr(statsObject, "riskset")
  risk_sets <- risk_sets %>% select(-'id')
  
  # Get the times
  time <- apollo$time
  
  # merge riskset with each timepoint
  combined <- merge(risk_sets, time, by = NULL)
  
  combined <- combined %>% rename("time" = "y")
  combined <- lapply(combined, as.numeric)
  combined <- as.data.frame(combined)
  
  # Create matrices for subtraction to make a status column for coxph
  combined_matrix <- data.matrix(combined)
  matrix_rows <- nrow(combined)
  
  repeated_df <- apollo[rep(seq_len(nrow(apollo)), each = 240), ] 
  repeated_df <- repeated_df[, c(2,3,1)]
  apollo_matrix <- data.matrix(repeated_df)
  
  status_matrix <- apollo_matrix - combined_matrix
  
  # create a status column
  status <- as.integer(rowSums(status_matrix == 0) == ncol(status_matrix))
  status <- as.data.frame(status)
  
  # Add status to the combined set
  combined <- cbind(combined, status)
  
  # Extract statistics and add them to the dataframe
  reciprocity <- statsObject[,,1]
  indegreeSender <- statsObject[,,2]
  outdegreeReceiver <- statsObject[,,3]
  
  combined$reciprocity <- c(reciprocity)
  combined$indegreeSender <- c(indegreeSender)
  combined$outdegreeReceiver <- c(outdegreeReceiver)
  
  return(combined)
}
```

##Fully observed data
```{r}
###### TRUE ANALYSIS
true.reh <- remify(edgelist = apollo, 
                   model = "tie")
# calculate stats
stats <- remstats(tie_effects = effects, 
                  reh = true.reh)
# use the function to create the correct format of the dataframe
true.cox.set <- prepare_coxph_data(stats, apollo)
# fit cox model 
true.cox.fit <- coxph(Surv(time, status) ~ reciprocity + indegreeSender + 
                        outdegreeReceiver, 
                      data=true.cox.set)
true <- coefficients(true.cox.fit)

true.cox.fit
```

##Analysis on time (interpolated), actor 1 + 2 MI
```{r}
###### Running the REM on  simulations
Results1 <- 
  mbased_finite_apollo[1:10] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
    )

Results1
```


```{r}
Results2 <- 
  mbased_finite_apollo[11:20] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender +
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
    )
```

```{r}
Results3 <- 
  mbased_finite_apollo[21:30] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results4 <- 
  mbased_finite_apollo[31:40] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results5 <- 
  mbased_finite_apollo[41:50] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results6 <- 
  mbased_finite_apollo[51:60] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results7 <- 
  mbased_finite_apollo[61:70] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results8 <- 
  mbased_finite_apollo[71:80] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results9 <- 
  mbased_finite_apollo[81:90] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```


```{r}
Results10 <- 
  mbased_finite_apollo[91:100] %>% 
  map(~.x %>% # for every simulation
        complete("all") %>% 
        map(~.x %>% # for every imputation
              stats_function() %>% # do stats function
              prepare_coxph_data(apollo = apollo) %$% # prepare cox ph
              coxph(Surv(time, status) ~ 
                      reciprocity + 
                      indegreeSender + 
                      outdegreeReceiver)) %>%
        pool(custom.t = ".data$b + .data$b / .data$m") %>% # pool coefficients 
        .$pooled %>% # extract table of pooled coefficients
          mutate(true = true, # add true
                 df = m-1,  # correct df
                 riv = Inf, # correct riv
                 std.error = sqrt(t), # standard error
                 statistic = estimate / std.error, # test statistic
                 p.value = 2 * (pt(abs(statistic), 
                                   pmax(df, 0.001), 
                                   lower.tail = FALSE)), # correct p.value
                 `2.5 %` = estimate - qt(.975, df) * std.error, # lower bound CI
                 `97.5 %` = estimate + qt(.975, df) * std.error, # upper bound CI
                 cov = `2.5 %` < true & true < `97.5 %`, # coverage
                 bias = estimate - true) %>% # bias
          select(term, m, true, estimate, std.error, statistic, p.value, 
                 riv, `2.5 %`, `97.5 %`, cov, bias) %>% 
          column_to_rownames("term") # `term` as rownames
  )
```

##Combining Results
```{r}
##### Combining Results
Results <- list(Results1,
               Results2,
               Results3,
               Results4,
               Results5,
               Results6,
               Results7,
               Results8,
               Results9,
               Results10) %>%
  purrr::flatten()
```


##Save results
```{r}
#saving Results
save(Results, file = "TimeINT_A12_MI.RData")
```

##Percentage bias and average width
```{r}
##### Adding percentage bias and average width to the Results
#function for average width and percentage bias.
AW <- function(df) df[["97.5 %"]] - df[["2.5 %"]]
PB <- function(df) 100 * abs((df[["estimate"]] - df[["true"]]) / df[["true"]])


Results_with_extra <- lapply(Results, function(df) {
  df$PB <- PB(df)
  df$AW <- AW(df)
  df
})

###### Average sims
Reduce("+", Results_with_extra) / length(mbased_finite_apollo)

```
```{r}
##### Creating a list of all estimates for every statistic
reciprocity <- Results %>%
  map(~.x %>% .["reciprocity", ]) %>%
  do.call("rbind", .)

indegreeSender <- Results %>% 
  map(~.x %>% .["indegreeSender", ]) %>% 
        do.call("rbind", .)

outdegreeReceiver <- Results %>% 
  map(~.x %>% .["outdegreeReceiver", ]) %>% 
        do.call("rbind", .)
    
##### A density plot of all estimates for every statistic
stats <- list(outdegreeReceiver = outdegreeReceiver,
              indegreeSender = indegreeSender,
              reciprocity = reciprocity)

for (stat_name in names(stats)) {
  plot_data <- stats[[stat_name]]
  plot <- ggplot(plot_data, aes(x = estimate)) + 
    geom_density() + 
    labs(x = paste(stat_name, "estimates"), y = "Density") + 
    theme_classic()
  
  print(plot)
}

```



